On the presentation of orthogonal groups over polynomial rings

### 2019-07-02 dl-paper.tex
Minor fix

For $n\geq 1$ we define ``truncated'' Steinberg groups $\St^{\leq n}(\Phi, B)$ by the set of homogeneous Steinberg generators of degree $\leq n$ modulo Steinberg relations of degree $\leq n$.
The following lemma asserts that most of the relations of type $\text{R3}^\bot_{d,e}$ in this presentation of $\St^{\leq n}(\Phi, B)$ 
 are superfluous and can be omitted.
\begin{lemma}\label{superfluous-relations}
 For every simply-laced root system $\Phi$ of rank $\geq 3$ and every $n \geq 1$ one can exclude from
 the presentation of $\St^{\leq n}(\Phi, B)$ all relations of type $\text{R3}_{d,e}^\bot$ whenever $\max(0,d) + \max(0,e) > 1$.
\end{lemma}
\begin{proof}
For the proof we will need the following commutator identities:
\begin{align} \label{eq:H1ii} [xy, z] = {}^x[y, z] \cdot [x,z];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
 \label{eq:H1iii} [x,z] = 1 \text{ implies } [x, [y,z]] = [[x,y],{}^yz].& \end{align}

@@

\begin{lemma} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism. In particular, the obvious map $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism. \end{lemma}
\begin{proof}
 The special case $\Phi=\rA_{\geq 4}$ of the assertion has been proved by Tulenbayev (see~\cite[Lemma~3.3]{Tu83}) 
 and therefore can be used to deduce the assertion in the cases $\Phi=\rD_\ell,\rE_\ell$.

>>>>

For $n\geq 1$ we define ``truncated'' Steinberg group $\St^{\leq n}(\Phi, B)$ as the quotient of the free group generated by the set $\mathcal{X}_{\leq n}^\Phi$ of homogeneous Steinberg generators of degree $\leq n$ modulo the normal subgroup $\mathcal{R}_{\leq n}^\Phi$ generated by the set of Steinberg relations of degree $\leq n$.

The following lemma asserts that most of the relations of type $\text{R3}^\bot_{d,e}$ of positive degree in this presentation of $\St^{\leq n}(\Phi, B)$ 
 are superfluous and can be omitted.
\begin{lemma}\label{superfluous-relations}
 For every simply-laced root system $\Phi$ of rank $\geq 3$ and every $n \geq 1$ one can exclude from
 the presentation of $\St^{\leq n}(\Phi, B)$ all relations of type $\text{R3}_{d,e}^\bot$ whenever $\max(0,d) + \max(0,e) > 1$.
\end{lemma}
\begin{proof}
For the proof we will need the following commutator identities:
\begin{align} \label{eq:H1ii} [xy, z] = {}^x[y, z] \cdot [x,z];&\\ %= [a,[b,c]]\cdot [b,c] \cdot [a,c];&\\
 \label{eq:H1iii} [x,z] = 1 \text{ implies } [x, [y,z]] = [[x,y],{}^yz].& \end{align}

@@

\begin{prop} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the map $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$ induced by the natural embedding of generators, is an isomorphism. In particular, the obvious map $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism. \end{prop}
\begin{proof}
 The special case $\Phi=\rA_{\geq 4}$ of the assertion has been proved by Tulenbayev (see~\cite[Lemma~3.3]{Tu83}) 
 and therefore can be used to deduce the assertion in the cases $\Phi=\rD_\ell,\rE_\ell$.
